MaxEnt: What is it good for?

### 2015-06-20 ms.tex
Niven

@@

\section*{Acknowledgements}
It is a pleasure to thank
Ariel Caticha (Albany),
Adom Giffin (Clarkson)
John Skilling (MaxEnt Data Consultants),
Carlos Rodriguez (Albany),
Stephen Gull (Cambridge),
Kevin Knuth (Albany),
Iain Murray (Edinburgh),
Anna Pancoast (UCSB),
Geraint Lewis (Sydney),
David Hogg (NYU),
Tom Loredo (Cornell),
Daniela Huppenkothen (NYU),
Peter Tuthill (Sydney),
and John Wilcox (Auckland)
for valuable discussions.

>>>>

{\bf Mention Niven and ``combinatorics'' -- it's just the sum rule then. not
a new principle}.

@@

\section*{Acknowledgements}
It is a pleasure to thank
Ariel Caticha (Albany),
Adom Giffin (Clarkson)
John Skilling (MaxEnt Data Consultants),
Carlos Rodriguez (Albany),
Stephen Gull (Cambridge),
Kevin Knuth (Albany),
Iain Murray (Edinburgh),
Anna Pancoast (UCSB),
Geraint Lewis (Sydney),
David Hogg (NYU),
Robert Niven (UNSW),
Tom Loredo (Cornell),
Daniela Huppenkothen (NYU),
Peter Tuthill (Sydney),
and John Wilcox (Auckland)
for valuable discussions.
